

#Task 1 Code
```{r packages}
# Add any additional packages you need to this chunk
library(tidyverse)
```

#Loadind data set
```{r dataset}
# Loading data here
asteroid <- read_csv("sbdb_query_results.csv")
asteroid
```

Ranking asteroids based on semi-major axis 

```{r task1}
rankby_a <- asteroid %>%
  arrange(abs(a)) %>% #a : semi-major axis distance
  slice(1:30) #see top 100 to confirm that data displays in ascending order

rankby_a
```


```{r task2}
rankby_per <- asteroid %>%
  arrange(abs(per_y)) %>% #a : semi-major axis distance
  slice(1:30) #see top 100 to confirm that data displays in ascending order

rankby_per
```
### Discussion
- By observation of the top 30 rankings, there is a close correlation between semi-major axis and orbital periods. This means that further asteroids from us tend to have higher orbital periods (take longer to orbit the sun) which is logical.
- We can go ahead and model the correlation between semi-major axis and the orbital period.
(a ~ per_y)
- ** we can later add more parameters (as predictor variables) and see if the model becomes more accurate for predicting a.

```{r }
#preparing dataset for model and fitting step

```









#Tricks for formatting presentation file
# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(DATASET), format = "html")
```

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs.